Openness and Computational Reproducibility in plant pathology: where do we stand and a way forward

### 2022-06-08 analysis/paper/paper.Rmd
Clean up libs being used

```{r, setup, echo = FALSE, message=FALSE}
packages <- c(
  "DiagrammeR",
  "DiagrammeRsvg",
  "bayesplot",
  "bayestestR",
  "brms",
  "dplyr",
  "egg",
  "english",
  "extrafont",
  "flextable",
  "ggplot2",
  "ggridges",
  "ggpubr",
  "here",
  "janitor",
  "knitr",
  "officer",
  "patchwork",
  "psych",
  "rsvg",
  "tidyr",
  "tools"
)

>>>>

```{r, setup, echo = FALSE, message=FALSE}
packages <- c(
  "DiagrammeR",
  "DiagrammeRsvg",
  "bayesplot",
  "bayestestR",
  "brms",
  "dplyr",
  "english",
  "extrafont",
  "flextable",
  "ggridges",
  "ggpubr",
  "here",
  "janitor",
  "knitr",
  "officer",
  "patchwork",
  "rsvg",
  "tidyr",
  "tools"
)
